Discovering causal factors with back-and-forth regression

### 2019-05-21 paper/paper.tex
wip: intro method

This is done by finding vectors $a$ and $b$ such that $Xa$ and $Yb$ display maximal correlation, or by maximizing $a'X'Yb$ over unit-normed $a$ and $b$.
%
To find a, one calculates the eigenvectors of (1).
%
The largest one is the direction with maximal correlation, the second one the maximal correlation direction orthogonal to the first, and so on.
%
For each canonical dimension, the corresponding eigenvalue is the square of the cosine between the corresponding direction along X and the subspace spanned by Y.

If (1) is diagonal, for instance in the model presented above, the features of X are eigenvectors.
%
If all eigenvalues are either 0 or 1, since they correspond to the squared cosine of the angle between the corresponding feature and the subspace spanned by Y, all the features are either part of the Y subspace (eigenvalues of one) or orthogonal to it (for zero eigenvalues).
%
Thus, back-and-forth regression amounts to CCA under the constraint that the subspaces spanned by X and Y are perpendicular, X is spanned by vectors of Y and vectors orthogonal to Y, and that the parallel and orthogonal components of X are spanned by disjoint sets of features of X.
%
The closer we are to this hypothesis, the closer the results of CCA and back-and-forth regression will be.

>>>>

This is done by finding vectors $a$ and $b$ such that $Xa$ and $Yb$ display maximal correlation, or by maximizing $a'X'Yb$ over unit-normed $a$ and $b$.
%
To find a, one calculates the eigenvectors of Eq. (1).
%
The largest one is the direction with maximal correlation, the second one the maximal correlation direction orthogonal to the first, and so on.
%
For each canonical dimension, the corresponding eigenvalue is the square of the cosine between the corresponding direction along X and the subspace spanned by Y.

If the result of Eq. (1) is diagonal, as in the model presented above, the features of X are eigenvectors.
%
If all eigenvalues are either 0 or 1, then all the features are either part of the Y subspace (eigenvalues of one) or orthogonal to it (for zero eigenvalues) because they correspond to the squared cosine of the angle between the corresponding feature and the subspace spanned by Y, .
%
Thus, back-and-forth regression amounts to CCA under the constraint that the subspaces spanned by X and Y are perpendicular, X is spanned by vectors of Y and vectors orthogonal to Y, and that the parallel and orthogonal components of X are spanned by disjoint sets of features of X.
%
The closer we are to this hypothesis, the closer the results of CCA and back-and-forth regression will be.
